Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-12-04 paper/snakemajoranas.tex
fix spelling

Where $\lambda_i$ are the eigenvalues of $A$.
Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
Then, since $\alpha$ is only defined in the postitive imagionary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a postitive imagionary part.
Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

>>>>

Where $\lambda_i$ are the eigenvalues of $A$.
Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
Then, since $\alpha$ is only defined in the positive imaginary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a positive imaginary part.
Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
